Toward single particle reconstruction without particle picking: Breaking the detection limit

### 2018-06-06 TEX/draft4.tex
Final comments for today

In general, for a signal $z$ of length $m$, the autocorrelation of order $q \geq 1$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
\begin{align}
	a_z^q[\ell_1,\ldots,\ell_{k-1}]  & = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
	\label{eq:ac_general}
\end{align}
where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
For our purposes, this will be applied both to $x_k$'s (each of length $L$) and to $y$ (of length $N$).
Explicitly, the first-, second- and third-order autocorrelations are given by
\begin{align} 
	a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
	a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
	a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
\end{align}
The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
\begin{align*}
	a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
\end{align*}
%Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.
Taking these symmetries into consideration, one can show that $a_z^1, a_z^2$ and $a_z^3$ contain \TODO{TKTK} (respectively) non-trivial distinct real numbers, generically.

@@

@@

\paragraph{Second numerical experiment.}
For the 1-D experiment, we worked with three signals of length $L = 21$ and generated the data in the same way as in the 2-D example.
The only difference is that here, for each
placement, one of the three signals is picked at random proportionally to the desired number
of occurrences of each.
In this experiment, we computed the first three autocorrelation functions. 
We do not assume to know the number of occurrences of each signal $\gamma_i$ ahead and we removed the biased terms (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$ either. 
\TODO{In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the first three autocorrelation functions. -- Was this removed? I can't find it.}

>>>>

In general, for a signal $z$ of length $m$, the autocorrelation of order $q \geq 1$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
\begin{align}
	a_z^q[\ell_1,\ldots,\ell_{k-1}]  & = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
	\label{eq:ac_general}
\end{align}
where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
For our purposes, this will be applied both to $x_k$'s (each of length $L$) and to $y$ (of length $N$).
Explicitly, the first-, second- and third-order autocorrelations are given by
\begin{align} 
	a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
	a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
	a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
\end{align}
The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
\begin{align*}
	a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
\end{align*}
%Additionally, if the moments of the signal depend only on the difference between the indices (Toeplitz structure), then they are equivalent to the autocorrelation functions.
Taking these symmetries into consideration, one can show that $a_z^1, a_z^2$ and $a_z^3$ contain \TODO{TKTK--I think it was commented in the latex} (respectively) non-trivial distinct real numbers, generically.

@@

\TODO{It would be more natural to present the 1D XP first given everything that preceeds, then to present the 2D XP, where we can explain it's a pretty special case.}

@@

\paragraph{Second numerical experiment.}

\TODO{I had a quite precise explanation of this experiment in the latex. Was it changed because we need to shorten, or is length not an issue? Nature Method's website states the methods section should give enough details for someone to be able to reproduce the experiment.}

For the 1-D experiment, we worked with three signals of length $L = 21$ and generated the data in the same way as in the 2-D example.
The only difference is that here, for each
placement, one of the three signals is picked at random proportionally to the desired number
of occurrences of each.
In this experiment, we computed the first three autocorrelation functions. 
We do not assume to know the number of occurrences of each signal $\gamma_i$ ahead and we removed the biased terms (see~\eqref{eq:data_ac_k1}) so we do not need to know $\sigma$ either. 
\TODO{In Appendix~\ref{sec:theory} we provide an argument on the number of equations we get from the first three autocorrelation functions. -- Was this removed? I can't find it.}
